Meta-analysis

### 2019-10-15 05_MetaAnalysis.Rmd
Updated based on new data import method

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <- import_data()
```

@@

```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq() +
   coord_flip()
```

@@

```{r tebu_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          dose_ai_f1_g.ha,
          total_fungicide) %>%
   ggplot(aes(x = as.factor(dose_ai_f1_g.ha))) +
   xlab("Dose (g ai/ha)") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly, which has been shown by Kerry McKenzie's work as well.
Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing.m, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing.m), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacings using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>% 
   glimpse()
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(host_genotype, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

```{r variance}

# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(tebuconazole_trts = length(y_error.type))

# Trials using propiconazole
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole",
          row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(propiconazole_trts = length(y_error.type))
```

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          y_error.type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```

@@

   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$y_error.type <-
      "SamplingVariance"

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(#fungicide_ai == "tebuconazole",
      #row_spacing.m == 0.75,
      y_error.type == "stdev") %>%
   select(trial_ref) %>%
   distinct()

@@

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$y_error.type <-
   "SamplingVariance"
```

@@

```{r}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          is.na(y_error.type)) %>%
   select(trial_ref) %>%
   distinct()
```

@@

# method as described by Emerson
PM_MB_train <- PM_MB_means %>%
   filter(y_error.type == "SamplingVariance")

@@

# for (i in NATrials$trial_ref) {
#    #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
#    
#    Sv <-
#       (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
#    
#    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
#    PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
#       "SamplingVariance"
# }

@@

Emerson proposed I look at the between trial variation
```{r between_trial_variation}
levels(factor(PM_MB_means$Y_error.type))

PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error.type == "SamplingVariance",]
meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)

# find the mean and variance of each trial
PM_MB_means_T <- PM_MB_means %>%
   filter(Y_error.type == "SamplingVariance") %>%
   group_by(trial_ref) %>%
   summarise(trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
             ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)

@@

for(i in SV_Trials){
   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"Trial_variance"]
}
PM_MB_means$TrialVariance
# OR ?
PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")

>>>>

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <- import_data()

@@

```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   ggtitle(label = "Number of trials in which the\nspecified fungicide was used") +
   scale_colour_usq() +
   theme_usq() +
   coord_flip()
```

@@

```{r tebu_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          dose_ai.ha,
          total_fungicide) %>%
   ggplot(aes(x = as.factor(dose_ai.ha))) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows in most cases increased yield significantly. This finding has also been shown by Kerry McKenzie's work as well.
Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacings using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing == 0.75) %>% 
   glimpse()
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing == 0.75) %>%
   group_by(host_genotype, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

```{r variance}
# PM_MB_means$Y_error_type <- forcats::fct_explicit_na(PM_MB_means$Y_error_type, na_level = NA)
# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type) %>%
   summarise(tebuconazole_trts = length(Y_error_type))

# Trials using propiconazole
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole",
          row_spacing == 0.75) %>%
   group_by(trial_ref, location, Y_error_type) %>%
   summarise(propiconazole_trts = length(Y_error_type))
```

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing == 0.75,
          Y_error_type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```

@@

   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$yield_error <-
      Sv
   PM_MB_means[PM_MB_means$trial_ref == Trial2012, ]$Y_error_type <-
      "SamplingVariance"

@@

```{r stdev2SampVariance}
# subset data by those which describe the Yield error with standard deviation
Trials <- PM_MB_means %>%
   filter(#fungicide_ai == "tebuconazole",
      #row_spacing.m == 0.75,
      Y_error_type == "stdev") %>%
   select(trial_ref) %>%
   distinct()

@@

# and replacing the values in the dataset
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$yield_error <-
   Sv
PM_MB_means[PM_MB_means$trial_ref %in% Trials$trial_ref,]$Y_error_type <-
   "SamplingVariance"
```

@@

```{r}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          is.na(Y_error_type)) %>%
   select(trial_ref) %>%
   distinct()
```

@@

# method as described by Emerson
PM_MB_train <- PM_MB_means %>%
   filter(Y_error_type == "SamplingVariance")

@@

# for (i in NATrials$trial_ref) {
#    #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped
#    
#    Sv <-
#       (PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha` * paramA) + InterC
#    
#    PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
#    PM_MB_means[PM_MB_means$trial_ref == i,]$Y_error_type <-
#       "SamplingVariance"
# }

@@

Emerson proposed I look at the between trial variation
```{r between_trial_variation}
unique(PM_MB_means$Y_error_type)

PM_MB_means.SV <- PM_MB_means[PM_MB_means$Y_error_type == "SamplingVariance",]
meta_mean.GY <- mean(PM_MB_means.SV$grain_yield.t.ha.,na.rm = TRUE)

# find the mean and variance of each trial
PM_MB_means_T <- PM_MB_means %>%
   filter(Y_error_type == "SamplingVariance") %>%
   group_by(trial_ref) %>%
   summarise(trial_mean = mean(grain_yield.t.ha., na.rm = TRUE),
             BW_trial_variance = sd(grain_yield.t.ha., na.rm = TRUE) ^ 2
             ) # I am not sure I have calculated between trial variance or trial variance// Should I be using a denominator (N-1) or (N), sd by default uses (N-1)

# by excluding the standard deviation of each treatment I have discarded much of the variance. Should I simulate a larger number of samples for each treatment to reflect the sample distribution of each treatment and then take the mean and standard deviation of the whole trial of the simulated data?

@@

for(i in SV_Trials){
   PM_MB_means[PM_MB_means$Trial_ref == i, "TrialVariance"] <- PM_MB_means_T[PM_MB_means_T$Trial_ref == i,"BW_trial_variance"]
}
PM_MB_means$TrialVariance
# OR ?
PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")
